---
title: "Structures"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Structures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
   collapse = TRUE,
   comment = "#>"
)

# Activate crayon
## https://github.com/r-lib/crayon/issues/24
options(crayon.enabled = TRUE)
old_hooks <- fansi::set_knit_hooks(
    knitr::knit_hooks,
    which = c("output", "message", "error")
)

structured:::local_test_directory()
```

The `structured` package revolves around the concept of strucures, which is a fancy name for project templates. Well, strongly *structured* project templates. So, to make the most of `structured`, it is essential to understand those structures to select the most adequate for your project.

Projects are mean to an end. Be it analyzing a dataset for a class project or creating a dashboard for a business. `structured` defines each kind of project by a combination of two values. The first is **project level** and determines **how complex** your project will be^[Usually complex problems demand complex solution (but simpler solutions are better!).]. The second is **analysis format** and specify **how** your project will solve the problem. The next sections give more details about each option those values can assume.

Before we start, it is important to load some packages. The `fs` package is necessary to show the projects directory tree.

```{r}
# Uncomment to install packages
## install.packages("fs")
## install.packages("remotes")
## remotes::install_github("GiuseppeTT/structured")

# Load packages
library(fs)
library(structured)
```

## Project level
### Basic
Text.

```{r}
structured:::local_test_directory()
structure_project(
    "basic-project",
    project_level = "Basic",
    analysis_format = "Script"
)
dir_tree("basic-project", all = TRUE)
```

### Intermediate
Text.

```{r}
structured:::local_test_directory()
structure_project(
    "intermediate-project",
    project_level = "Intermediate",
    analysis_format = "Script"
)
dir_tree("intermediate-project", all = TRUE)
```

## Analysis format
### Script
Text.

```{r}
structured:::local_test_directory()
structure_project(
    "script-project",
    project_level = "Basic",
    analysis_format = "Script"
)
dir_tree("script-project", all = TRUE)
```

### R Markdown
Text.

```{r}
structured:::local_test_directory()
structure_project(
    "r-markdown-project",
    project_level = "Basic",
    analysis_format = "R Markdown"
)
dir_tree("r-markdown-project", all = TRUE)
```

### R Markdown (Structured)
Text.

```{r}
structured:::local_test_directory()
structure_project(
    "r-markdown-structured-project",
    project_level = "Basic",
    analysis_format = "R Markdown (Structured)"
)
dir_tree("r-markdown-structured-project", all = TRUE)
```

### Shiny
Text.

```{r}
structured:::local_test_directory()
structure_project(
    "shiny-project",
    project_level = "Basic",
    analysis_format = "Shiny"
)
dir_tree("shiny-project", all = TRUE)
```
