---
title: "Structures"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Structures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)

root <- tempfile()
dir.create(root)
knitr::opts_knit$set(
    root.dir = root
)

# Activate crayon
## https://github.com/r-lib/crayon/issues/24
options(crayon.enabled = TRUE)
old_hooks <- fansi::set_knit_hooks(
    knitr::knit_hooks,
    which = c("output", "message", "error")
)
```

The `structured` package revolves around the concept of strucures, which is a fancy name for project templates. Well, strongly *structured* project templates. So, it is essential to understand those structures to select the most adequate for your project.

Project is a means to an end. Be it analyzing a dataset for a class project or creating a dashboard for a business. `structured` defines each kind of project by a combination of two values. The first is **project level** and determines **how complex** your project will be^[Usually, complex problems demand complex solution.]. The second is **analysis format** and specifies **how** your project will solve the problem. The next sections give more details about each option those values can assume.

Before we start, it is important to load some packages.

```{r}
# Uncomment to install packages
## install.packages("fs")
## install.packages("remotes")
## remotes::install_github("GiuseppeTT/structured")

# Load packages
library(fs)
library(structured)
```

## Project level
### Basic
Except for the `analysis.R` file^[The `analysis.R` file comes from the "script analysis format", which is the default analysis format value. It is included because `structure_project()` needs both `project_level` and `analysis_format` supplied.], the "basic project level" structure has the following files:

```{r}
structure_project(
    "basic-project",
    project_level = "Basic",
    analysis_format = "Script"
)
dir_tree("basic-project", all = TRUE)
```

This structure is simple, minimal, but complete enough to accomodate all the analysis formats. In other words, a perfect starting point for newbies and an excelent use for quick and simple projects.

The purpose of each file/folder is the following:

- `data/` Save all the pertaining data. For example csv tabular data, the cleaned version of the csv tabular data or even a SQLite database file.

- `output/` Save anything generated that isn't data. For instance figures, tables, models, reports, presentation, etc.

- `extra/` Save any file that isn't data, output or code but is related to the project. Some cases are professor instructions about the class project or some meeting notes.

- `R/` Save auxiliar R files. That is, files that are not run directly but are used by those run files. Some examples are `functions.R` (described next) and `ui.R` and `sever.R` used by {shiny}.

- `R/functions.R` Write your R functions used in the rest of the project.

- `basic-project.Rproj` (`<project-directory>.Rproj`) RStudio project file. This [article](https://www.tidyverse.org/blog/2017/12/workflow-vs-script/) from Jenny Brian and this [chapter](https://r4ds.had.co.nz/workflow-projects.html) from R For Data Science book are great reference. In short, this little guy allows you to break free from all the evil that comes from `setwd("obscure/path/that/only/works/in/my/notebook")` and use `read_csv("data/my-data.csv")`.

Compared to a single folder with all of your files thrown into, this structure keeps both your files organized with the subdirectories and your code clean with the `R/` folder so you can modularize your code.

### Intermediate
In addition to the files from the previous project level, the "indermediate project level" structure posses a `.gitignore` and a `README.md`.

```{r}
structure_project(
    "intermediate-project",
    project_level = "Intermediate",
    analysis_format = "Script"
)
dir_tree("intermediate-project", all = TRUE)
```

The purpose of each file/folder is the following:

- `README.md`

- `.gitignore`

## Analysis format
### Script
Text.

```{r}
structure_project(
    "script-project",
    project_level = "Basic",
    analysis_format = "Script"
)
dir_tree("script-project", all = TRUE)
```

### R Markdown
Text.

```{r}
structure_project(
    "r-markdown-project",
    project_level = "Basic",
    analysis_format = "R Markdown"
)
dir_tree("r-markdown-project", all = TRUE)
```

### R Markdown (Structured)
Text.

```{r}
structure_project(
    "r-markdown-structured-project",
    project_level = "Basic",
    analysis_format = "R Markdown (Structured)"
)
dir_tree("r-markdown-structured-project", all = TRUE)
```

### Shiny
Text.

```{r}
structure_project(
    "shiny-project",
    project_level = "Basic",
    analysis_format = "Shiny"
)
dir_tree("shiny-project", all = TRUE)
```
